What is MaxEnt?

### 2015-06-14 ms.tex
back to discrete

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}

@@

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a prior distribution $q(\boldsymbol{x})$ describing a state of
knowledge about a vector of quantities $\boldsymbol{x}$. Consider some
function of the unknowns, such as $F=f(\boldsymbol{x}) = \sum_{i=1}^N x_i$.
If the value of $F$ is known, then our distribution for $\boldsymbol{x}$ can
be updated as in Section~\ref{sec:bayes}. If we receive testable information
about the expected value of $F$, then our distribution for $\boldsymbol{x}$ can
be updated as in Section~\ref{sec:expectations}.

In this section we'll look at a different kind of testable information that
relates to $f$, but is not the expected value. What if we receive testable
information about the marginal distribution for $f$?

For any distribution $p(\boldsymbol{x})$, the marginal distribution for $F$ is:
\begin{eqnarray}
p(F) &=& \int \delta\left(F - f(\boldsymbol{x})\right)p(\boldsymbol{x}) \, d^n \boldsymbol{x}\label{eqn:constraint}
\end{eqnarray}
If $p(F)$ is a specified function, this is an infinite number of expected
value constraints on $p(\xx)$. Therefore the probability distribution
$p(\xx)$ with maximum entropy with respect to $q(\xx)$ that satisfies the
constraint~\ref{eqn:constraint} is:
\begin{eqnarray}
p(\xx) &=& \frac{q(\xx)}{Z}\exp\left[- \right]
\end{eqnarray}

>>>>

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm]{geometry}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}

@@

\section{MaxEnt and Hierarchical Bayesian Models}
Suppose we have a discrete prior distribution $q(\xx)$. Consider some
function of the unknown quantity, $f(\xx)$.
If the value of $F$ is known, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:bayes}. If we receive testable information
about the expected value of $F$, then our distribution for $\xx$ can
be updated as in Section~\ref{sec:expectations}.

In this section we'll look at a different kind of testable information that
relates to $F$, but is not the expected value. What if we receive testable
information about the marginal distribution for $F$?

For any distribution $p(\xx)$, the marginal distribution for $F$ is:
\begin{eqnarray}
p(F) &=& \sum_{\xx}\mathds{1}\left(f(\xx) = F\right)p(\xx)\label{eqn:constraint}
\end{eqnarray}
If $p(F)$ is a specified function, this is an infinite number of expected
value constraints on $p(\xx)$. Therefore the probability distribution
$p(\xx)$ with maximum entropy with respect to $q(\xx)$ that satisfies the
constraint~\ref{eqn:constraint} is:
\begin{eqnarray}
p(\xx) &=& \frac{q(\xx)}{Z}\exp\left[- \right]
\end{eqnarray}
